Human Capital Model

### 2016-02-01 Tex/paper.tex
123

The temperature water in the bathtub is a relatively

\item \textbf{assumption 5} For the promotion probability and
  organization change, the other factors effects the churn probability
  is invariable.

Though churn derives from varieties of reasons and they are actually
lacking of known conditions and data to estimate them, we have to
regard it as stable in our model.

\item \textbf{assumption 6} Each division or office have at least one
  middle manager or senior manager.

\end{itemize}

>>>>

Since the temperature of water in the bathtub is relatively uniform, the slight convection won't influence heat exchange.

\item \textbf{assumption 5} Water, bathtub, person and the surrounding air compose a closed heat system.
\end{itemize}
